---
title: "Analysis v0"
output: html_document
date: "2022-11-29"
---

Input from "C:/Users/npr8/OneDrive - USNH/2022---Household-PULSE-Data-Analysis 2/01---PULSE_EW-NT-20221021 EW fullset"

```{r setup, include=FALSE, warning=FALSE, error=FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readxl)
library(scales)
library(plotly)
library(ggrepel) 
```

# Read in data

```{r}
df <- read_csv("../../PULSE_vis_setting.csv") %>%
  inner_join(read.csv('../../week.csv'), by='WEEK') %>%
  mutate(date = as.Date(date, format('%m/%d/%Y')))
df %>% tail()
```

# Line plot

```{r}
tot_workers <- df %>% 
  filter(F_shot == 1 & lbl_anywork=='Yes') %>%
  group_by(date) %>%
  summarise(Population = sum(WgtFreq)) %>%
  mutate(lbl_setting = "Total Workers",
         lbl_wkvol = NA,
         lbl_anywork = NA) %>%
  
union(

df %>%
  filter(F_shot == 1 & lbl_anywork=='Yes') %>%
  group_by(date,lbl_anywork,lbl_wkvol,lbl_setting) %>%
  summarise(Population = sum(WgtFreq)) %>%
  mutate(lbl_setting = str_replace(lbl_setting,'\x93',''),
         lbl_setting = str_replace(lbl_setting,'\x94',''),
         lbl_setting = 
           ifelse(lbl_wkvol=='No' & !is.na(lbl_wkvol),'Workers at home',lbl_setting),
         lbl_setting = 
           ifelse((lbl_wkvol=='Yes' & lbl_setting=='Missing Data'  & !is.na(lbl_wkvol)),'No Industry Response',lbl_setting))

) %>% 
  
  filter(!is.na(lbl_setting)) %>%
  mutate(lbl_setting = ifelse(nchar(lbl_setting)>65,paste(str_sub(lbl_setting,1,65),"...",sep = ""),lbl_setting))
#https://www.cdc.gov/museum/timeline/covid19.html

Vaccination_figure1 <- ggplot(data= tot_workers , aes(x=date, y=Population, color=lbl_setting)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=75E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=75E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure1
```


```{r}
setting_filter <- c('Total Workers', 'Workers at home','None of the above','Other job deemed essential during the COVID-19 pandemic',
                    'Healthcare (e.g., hospital, doctor, dentist or mental health specialist office, outpatient facility, long-term care, home health care, pharmacy, medical laboratory)')


Vaccination_figure1a <- ggplot(data= tot_workers %>%
                                filter(lbl_setting %in% setting_filter)
                              , aes(x=date, y=Population, color=lbl_setting)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=75E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=75E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure1a
```


```{r}
Vaccination_figure1b <- ggplot(data= tot_workers %>%
                                filter(!(lbl_setting %in% setting_filter))
                              , aes(x=date, y=Population, color=lbl_setting)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=12E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=12E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure1b
```


Individual Industry lines...

```{r}
tot_workers_only <- df %>% 
  filter(lbl_anywork=='Yes') %>%
  group_by(date,F_shot) %>%
  summarise(Population = sum(WgtFreq)) %>%
  mutate(lbl_setting = "Total Workers",
         lbl_wkvol = NA,
         lbl_anywork = NA)

Vaccination_figure2 <- ggplot(data= tot_workers_only, aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=100E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=100E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure2
```

```{r}
df <- df %>% 
  mutate(lbl_setting = 
           ifelse(lbl_wkvol=='No' & !is.na(lbl_wkvol),'Workers at home',lbl_setting))

tot_workers_only_percent <- df %>% 
  filter(lbl_anywork=='Yes' & F_shot=='Total') %>%
  group_by(date) %>%
  summarise(Population = sum(WgtFreq)) %>%
  left_join(df %>%filter(lbl_anywork=='Yes'), by=c('date')) %>%
  group_by(date,F_shot) %>%
  summarise(Percent = sum(WgtFreq)/Population) %>%
  mutate(lbl_setting = 'Total Workers') %>% unique()

tot_workers_only_percent_CI <- read.csv('../../PULSE_vis_anywork.csv') %>%
  filter(lbl_anywork=='Yes') %>%
  inner_join(read.csv('../../week.csv'), by='WEEK') %>%
  mutate(date = as.Date(date, format('%m/%d/%Y')),
         lbl_setting = 'Total Workers',
         Percent = Percent/100,
         UpperCI = Percent + qnorm(0.975)*as.double(StdErr)/100,
         LowerCI = Percent - qnorm(0.975)*as.double(StdErr)/100) %>%
  select(date,F_shot,lbl_setting,LowerCI,UpperCI)

tot_workers_only_percent <- tot_workers_only_percent %>%
  ungroup() %>%
  inner_join(tot_workers_only_percent_CI, by=c('date','F_shot','lbl_setting'))


ggplot(data= tot_workers_only_percent %>% filter(F_shot == '1'), aes(x=date, y=Percent, linetype = lbl_setting)) + 
  geom_line() + 
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.5), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.5), color="black", angle=90) +
  geom_hline(yintercept=0,color='light gray') + 
  geom_ribbon(aes(ymin = LowerCI, ymax = UpperCI), alpha = 0.2)
  ggtitle("Total Workers") + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
  theme(axis.text.x=element_text(angle=60, hjust=1))
```

```{r}
ind_workers <- df %>% 
  filter(lbl_anywork=='Yes') %>%
  mutate(lbl_setting = str_replace(lbl_setting,'\x93',''),
         lbl_setting = str_replace(lbl_setting,'\x94',''),
         lbl_setting = ifelse(nchar(lbl_setting)>65,paste(str_sub(lbl_setting,1,65),"...",sep = ""),lbl_setting),
         lbl_setting = 
           ifelse(lbl_wkvol=='No' & !is.na(lbl_wkvol),'Workers at home',lbl_setting)) %>%
  group_by(date,F_shot,lbl_setting) %>%
  summarise(Population = sum(WgtFreq))

workers_only_percent <- df %>% 
  filter(lbl_anywork=='Yes' & F_shot=='Total') %>%
  group_by(date, lbl_setting) %>%
  summarise(Population = sum(WgtFreq)) %>%
  left_join(df%>%filter(lbl_anywork=='Yes'), by=c('date','lbl_setting')) %>%
  group_by(date,F_shot,lbl_setting) %>%
  summarise(Percent = sum(WgtFreq)/Population) %>%
  mutate(lbl_setting = str_replace(lbl_setting,'\x93',''),
         lbl_setting = str_replace(lbl_setting,'\x94',''),
         lbl_setting = ifelse(nchar(lbl_setting)>65,paste(str_sub(lbl_setting,1,65),"...",sep = ""),lbl_setting))
 
workers_only_percent_CI <- read.csv('../../PULSE_vis_setting.csv') %>%
  filter(lbl_anywork=='Yes') %>%
  inner_join(read.csv('../../week.csv'), by='WEEK') %>%
  mutate(date = as.Date(date, format('%m/%d/%Y')),
         Percent = Percent/100,
         UpperCI = Percent + qnorm(0.975)*as.double(StdErr)/100,
         LowerCI = Percent - qnorm(0.975)*as.double(StdErr)/100,
         lbl_setting = str_replace(lbl_setting,'\x93',''),
         lbl_setting = str_replace(lbl_setting,'\x94',''),
         lbl_setting = ifelse(nchar(lbl_setting)>65,paste(str_sub(lbl_setting,1,65),"...",sep = ""),lbl_setting),
         lbl_setting = 
           ifelse(lbl_wkvol=='No' & !is.na(lbl_wkvol),'Workers at home',lbl_setting)) %>%
  select(date,F_shot,lbl_setting,LowerCI,UpperCI)

workers_only_percent <- workers_only_percent %>%
  inner_join(workers_only_percent_CI, by=c('date','F_shot','lbl_setting'))
```

Healthcare workers

```{r}
Vaccination_figure3 <- ggplot(data= ind_workers %>%
                                filter(grepl('Healthcare (e.g., ',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=10E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=10E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure3
```

```{r}
proportion_chart_gen <- function(data, title){
  ggplot(data= data, aes(x=date, y=Percent, linetype = lbl_setting)) + 
  geom_text(aes(x=as.Date('2021-02-03'), label="Phase 3", y=0.1), color="light grey") +
  geom_rect(aes(xmin=as.Date('2021-04-14'), xmax=as.Date('2021-07-21'), ymin=0, ymax=Inf), alpha=0.05, fill = 'light grey') +
  geom_text(aes(x=as.Date('2021-05-26'), label="Phase 3.1", y=0.1), color="dark grey") +
  geom_text(aes(x=as.Date('2021-09-15'), label="Phase 3.2", y=0.1), color="light grey") +
  geom_rect(aes(xmin=as.Date('2021-12-13'), xmax=as.Date('2022-03-14'), ymin=0, ymax=Inf), alpha=0.05, fill = 'light grey') +
  geom_text(aes(x=as.Date('2022-01-26'), label="Phase 3.3", y=0.1), color="dark grey") +
  geom_text(aes(x=as.Date('2022-04-27'), label="Phase 3.4", y=0.1), color="light grey") +
  geom_rect(aes(xmin=as.Date('2022-06-01'), xmax=as.Date('2022-09-14'), ymin=0, ymax=Inf), alpha=0.05, fill = 'light grey') +
  geom_text(aes(x=as.Date('2022-07-27'), label="Phase 3.5", y=0.1), color="dark grey") +
  geom_text(aes(x=as.Date('2022-10-12'), label="Phase 3.6", y=0.1), color="light grey") +
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.5), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.5), color="black", angle=90) +
  geom_ribbon(aes(ymin = LowerCI, ymax = UpperCI), alpha = 0.2) +
  scale_color_discrete(name="") +
  scale_linetype_discrete(name="") +
  geom_hline(yintercept=0,color='light gray') + 
  guides(color = FALSE, size = FALSE) + 
  ggtitle(title) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y") +
  theme(axis.text.x=element_text(angle=60, hjust=1))
}

chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Healthcare (e.g., ',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Social Services workers

```{r}
Vaccination_figure4 <- ggplot(data= ind_workers %>%
                                filter(grepl('Social service (e.g., ',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=3.75E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=3.75E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure4
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Social service (e.g., ',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Preschool or daycare workers

```{r}
Vaccination_figure5 <- ggplot(data= ind_workers %>%
                                filter(grepl('Preschool or daycare',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=1.2E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=1.2E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure5
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Preschool or daycare',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

K-12 workers

```{r}
Vaccination_figure6 <- ggplot(data= ind_workers %>%
                                filter(grepl('K-12 school',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=1.2E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=1.2E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure6
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('K-12 school',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Other schools and instructional settings (e.g. 

```{r}
Vaccination_figure7 <- ggplot(data= ind_workers %>%
                                filter(grepl('Other schools and instructional settings (e.g. ',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=1.2E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=1.2E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure7
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Other schools and instructional settings (e.g. ',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

First response (e.g.

```{r}
Vaccination_figure8 <- ggplot(data= ind_workers %>%
                                filter(grepl('First response (e.g.',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=1.2E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=1.2E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure8
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('First response (e.g.',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Death care (e.g.

```{r}
Vaccination_figure9 <- ggplot(data= ind_workers %>%
                                filter(grepl('Death care (e.g.',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.3E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.3E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure9
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Death care (e.g.',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Correction facility (e.g.

```{r}
Vaccination_figure10 <- ggplot(data= ind_workers %>%
                                filter(grepl('Correctional facility (e.g.',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure10
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Correctional facility (e.g.',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Food and beverage store (e.g.

```{r}
Vaccination_figure11 <- ggplot(data= ind_workers %>%
                                filter(grepl('Food and beverage store (e.g.',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=6E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=6E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure11
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Food and beverage store (e.g.',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Agriculture, forestry, 

```{r}
Vaccination_figure12 <- ggplot(data= ind_workers %>%
                                filter(grepl('Agriculture, forestry, ',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure12
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Agriculture, forestry, ',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Food manufacturing facility (e.g.

```{r}
Vaccination_figure13 <- ggplot(data= ind_workers %>%
                                filter(grepl('Food manufacturing facility (e.g., meat-',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure13
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Food manufacturing facility (e.g., meat-',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Non-food manufacturing facility (e.g.

```{r}
Vaccination_figure14 <- ggplot(data= ind_workers %>%
                                filter(grepl('Non-food manufacturing facility (e.g. metals',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure14
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Non-food manufacturing facility (e.g. metals',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Public transit (e.g., bus

```{r}
Vaccination_figure15 <- ggplot(data= ind_workers %>%
                                filter(grepl('Public transit (e.g., bus',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure15
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Public transit (e.g., bus',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

United States Postal Service

```{r}
Vaccination_figure16 <- ggplot(data= ind_workers %>%
                                filter(grepl('United States Postal Service',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure16
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('United States Postal Service',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Other job deemed “essential” during the COVID-19 pandemic

```{r}
Vaccination_figure17 <- ggplot(data= ind_workers %>%
                                filter(grepl('Other job deemed essential',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.4E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.4E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure17
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Other job deemed essential',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])

Vaccination_figure17a <- ggplot(data= tot_workers_only_percent %>% union(workers_only_percent %>% filter(grepl('Other job deemed essential',lbl_setting, fixed=TRUE))), aes(x=date, y=Percent, color=F_shot, linetype = lbl_setting)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.8), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.8), color="black", angle=90) +
  scale_color_discrete(name="") +
  scale_linetype_discrete(name="") +
  geom_hline(yintercept=0,color='light blue')

Vaccination_figure17a
```

None of the above

```{r}
Vaccination_figure18 <- ggplot(data= ind_workers %>%
                                filter(grepl('None of the above',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=20E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=20E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure18
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('None of the above',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

Workers at home

```{r}
Vaccination_figure19 <- ggplot(data= ind_workers %>%
                                filter(grepl('Workers at home',lbl_setting, fixed=TRUE)), aes(x=date, y=Population, color=F_shot)) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=20E6), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=20E6), color="black", angle=90) +
  scale_color_discrete(name="")

Vaccination_figure18
```

```{r}
chart_temp <- tot_workers_only_percent %>% 
  union(workers_only_percent %>% filter(grepl('Workers at home',lbl_setting, fixed=TRUE))) %>% 
  filter(F_shot == '1')

proportion_chart_gen(chart_temp, 
                     chart_temp$lbl_setting %>% unique() %>%.[2])
```

```{r}
workers_only_percent %>% ungroup() %>% select(lbl_setting) %>% unique()
```
