---
title: "SHV"
output: html_document
date: "2022-12-01"
---

Reference: 
https://rstudio-pubs-static.s3.amazonaws.com/382648_93783f69a2fd4df98ade8751c21abbad.html
https://www.cdc.gov/museum/timeline/covid19.html
https://www.ncsl.org/research/health/first-covid-19-vaccine-administered-in-the-u-s-magazine2020.aspx

I'd propose the following model for estimating parameters related to vaccine propagation. 
$N$: total population
$V$: vaccinated
$H$: hesitant
$S$: susceptible but not vaccinated
$$N = V+S+H$$

$$1 = \frac{S(t)}{N(t)} +  \frac{V(t)}{N(t)} + \frac{H(t)}{N(t)}$$
$$h(t) = \frac{H(t)}{N(t)}$$
$$s(t) = \frac{H(t)}{N(t)}$$
$$v(t) = \frac{V(t)}{N(t)}$$
One can then estimate three parameters the initial proportion of hesitant $h(0)$, the vaccination rate $\hat{\beta}$, and presumed increase in vaccine hesitancy $\hat{\gamma}$, rate of reported vaccination  $\hat{\alpha}$ (related to either changes in demographics or vaccination response willingness) and p the proportion split of those dropping off that join the potential Susceptible and Hesitant groups:

$$\frac{ds}{dt} = -\beta S V -\gamma H S$$

$$\frac{dh}{dt} = \gamma H S $$

$$\frac{dv}{dt} = \beta S V $$

```{r}
library(deSolve)
library(lubridate)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(bbmle)
```

SIR dataset:

```{r}
df <- read_csv("../../PULSE_vis_setting.csv") %>%
  inner_join(read.csv('../../week.csv'), by='WEEK') %>%
  mutate(date = as.Date(date, format('%m/%d/%Y')))

tot_workers_only_percent <- df %>% 
  filter(lbl_anywork=='Yes' & F_shot=='Total') %>%
  group_by(date) %>%
  summarise(Population = sum(WgtFreq)) %>%
  left_join(df%>%filter(lbl_anywork=='Yes'), by=c('date')) %>%
  group_by(date,F_shot) %>%
  summarise(Percent = sum(WgtFreq)/Population) %>%
  mutate(lbl_setting = 'Total Workers') %>% unique()

weeks <- data.frame('date' = as.Date('2020-12-30') + seq(1:99)*7)

SHV <- tot_workers_only_percent %>%
  select(-c(lbl_setting)) %>%
  pivot_wider(id_cols = date ,names_from = F_shot, values_from = Percent) %>%
  mutate(date = as.Date(ifelse(date == as.Date('2021-01-05') | date == as.Date('2021-02-02'),date+1,date), origin='1970-01-01')) %>%
  right_join(weeks, by = 'date') %>%
  arrange(date) %>%
  ungroup() %>%
  fill(c(`0`,`1`,Total), .direction = 'down')

SHV %>% write.csv('raw_SHV.csv')
```

# Create simulator

```{r}
s_1 <- function(beta, gamma, S0, H0, V0, times) {
  require(deSolve) # for the "ode" function
  
  # the differential equations:
  s_equation <- function(time, variables, parameters) {
  with(as.list(c(variables, parameters)), {
    dS <- - beta * S * V - gamma * H * S 
    dH <- + gamma * H * S 
    dV <- + beta * S * V 
      return(list(c(dS, dH, dV)))
  })
  }
    
  # the parameters values:
  parameters_values <- c(beta  = beta, gamma = gamma)
  
  # the initial values of variables:
  initial_values <- c(S = S0, H = H0, V = V0)
  
  # solving
  out <- ode(initial_values, times, s_equation, parameters_values)

# returning the output:
  as.data.frame(out)
}

s_1
```


```{r}
ss <- function(beta, gamma, alpha, p, H0, data = SHV) {
  S0 <- data$`0`[1] - H0
  V0 <- data$`1`[1]
  times <- seq(1:length(data$date))-1
  predictions <- s_1(beta = beta, gamma = gamma,     # parameters
                       H0 = H0,
                       S0 = S0, # variables' intial values
                       V0 = V0,
                       times = times)                # time points
  sum(((predictions$S[-1]+predictions$H[-1]) - data$`0`[-1])^2)
}

ss2 <- function(x) {
  ss(beta = x[1],gamma = x[2], H0 = x[3])
}

starting_param_val <- c(0.7, 0.001, 0)
ss_optim <- optim(starting_param_val, ss2)

ss_optim
```

```{r}
predictions <- s_1(beta = ss_optim$par[1], gamma = ss_optim$par[2], 
    S0 = SHV$`0`[1]-ss_optim$par[3],
    H0 = ss_optim$par[3],
    V0 = SHV$`1`[1],
    times = seq(1:length(SHV$date))-1
    )

predictions%>%
  mutate(tot = S + H + V)

predS_sd <- sd(predictions$S)

plot(predictions$S)
```

```{r}
tot_workers_only_percent_pred <- SHV %>%
  mutate(Predictions = predictions$S + predictions$H,
         Hesitant = predictions$H) %>%
  pivot_longer(cols=c(`0`,`1`,Total,Predictions, Hesitant), names_to = "F_shot", values_to = "Percent")

SHV_figure1 <- ggplot(data= tot_workers_only_percent_pred, aes(x=date, y=Percent, color=c(F_shot))) + 
  geom_line() + 
  scale_y_continuous(labels = comma) +
  geom_vline(xintercept = as.Date('2021-06-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-06-01'), label="\nDelta becomes dominant variant", y=0.8), color="black", angle=90) +
  geom_vline(xintercept = as.Date('2021-12-01'), linetype='dashed') +
  geom_text(aes(x=as.Date('2021-12-01'), label="\nFirst US Omicron case", y=0.8), color="black", angle=90) +
  scale_color_discrete(name="") +
  geom_hline(yintercept=0,color='light blue')

SHV_figure1
```

# Normal Distribution of Errors

```{r}
mLL <- function(beta, gamma, H0, data = SHV) {
  S0 <- data$`0`[1] - H0
  V0 <- data$`1`[1]
  times <- seq(1:length(data$date))-1
  predictions <- s_1(beta = beta, gamma = gamma,     # parameters
                       H0 = H0,
                       S0 = S0, # variables' intial values
                       V0 = V0,
                       times = times)                # time points
  predictions <- predictions[-1,] # removing the first point too
  if (any(predictions < 0)) return(NA) # safety
# returning minus log-likelihood:
  -sum(dnorm(x = SHV$`0`[-1] - predictions$H, mean = predictions$S, sd=predS_sd, log = FALSE))
}

starting_param_val <- list(beta = ss_optim$par[1], gamma = ss_optim$par[2], H0 = ss_optim$par[3])
estimates <- mle2(minuslogl = mLL,
                       starting_param_val,
                       method = "Nelder-Mead")
```


```{r}
summary(estimates)
```

```{r}
prof <- profile(estimates)
plot(prof, main = NA)
```